Fast gravitational wave parameter estimation without compromises

### 2023-02-06 src/tex/ms.tex
typo

% More features such as marginalization
Furthermore, our current implementation is minimal and we do not make use of
most standard ``tricks'' to accelerate sampling.  In particular, we do not
incorporate (semi)analytic marginalization schemes over parameters such as time
and phase\cite{2019PASA...36...10T}. Because of the already reasonable
performance of our sampler thanks to hardware accelerators, time and phase
marginalization are not crucial, as the performance of our implementation is not
significantly impacted by having two extra dimensions. We also do not include
calibration uncertainties in this study because of simplicity reason. On top of that, since we are planning
to deploy this pipeline to near online PE, we also need to consider estimating
the PSD on the same timescale, which \cite{Cornish:2021wxy} have proposed
a solution for. We are looking into incorporating analytic marginalization
schemes, calibration uncertainties, and real-time PSD estimation in our code as
well.

>>>>

% More features such as marginalization
Furthermore, our current implementation is minimal and we do not make use of
most standard ``tricks'' to accelerate sampling.  In particular, we do not
incorporate (semi)analytic marginalization schemes over parameters such as time
and phase\cite{2019PASA...36...10T}. Because of the already reasonable
performance of our sampler thanks to hardware accelerators, time and phase
marginalization are not crucial, as the performance of our implementation is not
significantly impacted by having two extra dimensions. We also do not include
calibration uncertainties in this study because of simplicity reason. On top of that, since we are planning
to deploy this pipeline to perform nearly-online PE, we also need to consider estimating
the PSD on the same timescale, which \cite{Cornish:2021wxy} have proposed
a solution for. We are looking into incorporating analytic marginalization
schemes, calibration uncertainties, and real-time PSD estimation in our code as
well.
